The impact of cosmic variance on simulating weak lensing surveys

### 2014-09-29 Writeup/paper_v3.tex
S3 selected disk-like galaxies mentioned

%\newcommand{\rachel}[1]{{\textcolor{red}{#1}}}
\newcommand{\rachel}[1]{}
%\newcommand{\arun}[1]{{\textcolor{blue}{#1}}}
\newcommand{\arun}[1]{}
\newcommand{\claire}[1]{{\textcolor{green}{#1}}}
\def\a{\alpha}
\def\reff@jnl#1{{\rm#1\/}}

@@

\subsection{\sersicn}
For other morphological parameters, we do not compare the distributions themselves directly. For \sersic profile fits, it gets tricky since we truncate the \sersic index at 6. 
For \btt ratios, we force the value to be greater than 0.05 \arun{What exactly do we do here?}. We will understand the dependence of these quantities on environment by computing the median values in different redshift bins.
We choose median over mean since it is more robust to the truncation effects.
Figure(s) \ref{fig:median_sersicn} show the median of the \sersic index with and without taking into account of the luminosity evolution. Median values obtained using stellar mass selected samples are plotted alongside for reference.
We observe that the overdense regions tend to have higher \sersic index than the adjacent underdense ones.
Figure(s) \ref{fig:median_dvcbtt} show the variation of median \btt ratio with redshift. We see that the bulge component is more in overdense regions than in the underdense regions.
These two observations are consistent with each other since higher \sersic index implies higher bulge component which are typical in young galaxies found in overdense regions.
%We chose median over mean since \sersic n greater than 6 are truncated to 6. This affects the mean statistic more than the median.
\begin{figure}
 %\centering
 \includegraphics[width=1.0\columnwidth]{median_sersicn}
 \includegraphics[width=1.0\columnwidth]{median_sersicn2}
 \caption{Median values of the \sersic indices for volume-limited samples \s$1$ and \s$3$ are plotted (filled centers and thin errorbars) in left and right panels respectively for each redshift bin.
          Median values for the \s$2$ sample are plotted in both the panels (open centers and thick errorbars) in both the panels.
          The horizontal errorbars simply correspond to the binwidth while the vertical ones are $1\sigma$ errorbars obtained by bootstrapping.}
 \label{fig:median_sersicn}
\end{figure}

@@

In this study, we have shown that morphological parameters of galaxies depend on the local environments along the line of sight in a manner than affect Weak Lensing simulations.
In studies of Weak Lensing, one simulates galaxy images in a redshift slice by learning from the images in the same redshift bin of a training sample like COSMOS, which we have used for our analysis here.
The survey volume is broken up into multiple redshift slices and are classified as `overdense', `underdense' or `neutral' according to their local environment.
This is done by comparing the 1-D redshift distribution to some of the parametric models available in the literature. 
The incompleteness in the sample is minimized by constructing a volume limited sample either by imposing stellar mass cuts (\s$3$) or by imposing a luminosity cut. 
Further, depending on whether we have the cut fixed or evolve with redshift, we get two more volume limited samples \s$1$ and \s$2$ respectively. 
Morphological parameters are obtained by fitting a single \sersic profile to the images or by a two component (bulge+disk) fit. 
The morphological quantities of interest include axis ratios or equivalently the ellipticities, \sersic index and \btt ratios.

For all the three volume-limited samples, we compare the distributions of the axis-ratios of the galaxies in overdense and underdense regions and conclude that the distributions are different after performing statistical tests on them.
From the axis ratios, we compute ellipticities and find that the root mean squared value of the ellipticities of galaxies in a redshift bin vary significantly between the overdense and underdense regions.
Such a behavior is also observed when ellipticies are computed using second moments instead of parametric model fitting. \sersic index and \btt ratios also exhibit similar trends
with redshift based on the local environment.

>>>>

\newcommand{\rachel}[1]{{\textcolor{red}{#1}}}
%\newcommand{\rachel}[1]{}
\newcommand{\arun}[1]{{\textcolor{blue}{#1}}}
%\newcommand{\arun}[1]{}
\newcommand{\claire}[1]{{\textcolor{green}{#1}}}
\def\a{\alpha}
\def\reff@jnl#1{{\rm#1\/}}

@@

\subsection{Other morphological parameters}
For other morphological parameters such as the \sersic index and \btt ratio, we do not compare the distributions themselves directly. 
For \sersic profile fits, it gets tricky since we truncate the \sersic index at 6. 
For \btt ratios, we force the value to be between 0.05 and 0.95. %\arun{What exactly do we do here?}.
We will understand the dependence of these quantities on environment by computing the median values in different redshift bins.
We choose median over mean since it is more robust to the truncation effects.
Figure(s) \ref{fig:median_sersicn} show the median of the \sersic index with and without taking into account of the luminosity evolution. Median values obtained using stellar mass selected samples are plotted alongside for reference.
We observe that the overdense regions tend to have higher \sersic index than the adjacent underdense ones.
Figure(s) \ref{fig:median_dvcbtt} show the variation of median \btt ratio with redshift. We see that the bulge component is more in overdense regions than in the underdense regions.
These two observations are consistent with each other since higher \sersic index implies higher bulge component which are typical in young galaxies found in overdense regions.

In Figs.~\ref{fig:median_sersicn}, we see that the \sersic indices of mass selected sample (\s$3$) are systematically greater than those of the luminosity selected samples (\s$1$,\s$2$).
This is consistent with the \btt values being higher in \s$3$ than in \s$1$ or \s$2$ in Fig.~\ref{fig:median_dvcbtt}. This is not just an edge effect but can be seen from the distributions themselves 
that the mass selected sample doesn't include as many disk-like galaxies as in luminosity selected samples.
%We chose median over mean since \sersic n greater than 6 are truncated to 6. This affects the mean statistic more than the median.
\begin{figure}
 %\centering
 \includegraphics[width=1.0\columnwidth]{median_sersicn}
 \includegraphics[width=1.0\columnwidth]{median_sersicn2}
 \caption{Median values of the \sersic indices for volume-limited samples \s$1$ and \s$3$ are plotted (filled centers and thin errorbars) in left and right panels respectively for each redshift bin.
          Median values for the \s$2$ sample are plotted in both the panels (open centers and thick errorbars) in both the panels.
          The horizontal errorbars simply correspond to the binwidth while the vertical ones are $1\sigma$ errorbars obtained by bootstrapping.}
 \label{fig:median_sersicn}
\end{figure}

@@

In this study, we have shown that morphological parameters of galaxies depend on the local environments along the line of sight in a manner than affect Weak Lensing simulations.
In studies of Weak Lensing, one simulates galaxy images in a redshift slice by learning from the images in the same redshift bin of a training sample like COSMOS, which we have used for our analysis here.
The survey volume is broken up into multiple redshift slices and are classified as `overdense', `underdense' or `neutral' according to their local environment.
This is done by comparing the 1-D redshift distribution to some of the parametric models available in the literature. 
The incompleteness in the sample is minimized by constructing a volume limited sample either by imposing stellar mass cuts (\s$3$) or by imposing a luminosity cut. 
Further, depending on whether we have the cut fixed or evolve with redshift, we get two more volume limited samples \s$1$ and \s$2$ respectively. 
Morphological parameters are obtained by fitting a single \sersic profile to the images or by a two component (bulge+disk) fit. 
The morphological quantities of interest include axis ratios or equivalently the ellipticities, \sersic indices and \btt ratios.

For all the three volume-limited samples, we compare the distributions of the axis-ratios of the galaxies in overdense and underdense regions and conclude that the distributions are different after performing statistical tests on them.
From the axis ratios, we compute ellipticities and find that the root mean squared value of the ellipticities of galaxies in a redshift bin vary significantly between the overdense and underdense regions.
Such a behavior is also observed when ellipticies are computed using second moments instead of a parametric model fitting. \sersic index and \btt ratios also exhibit similar trends
with redshift based on the local environment.
